Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
merge and first paragraph of discussion

\section{Discussion}
\label{sec:discussion}

\subsection{Calling convention}
\textbf{Formulating control flow correctness} The attentive reader may notice
that, while we claim that our calling convention enforces control-flow
correctness, we do not prove a general theorem to show that this is the case.
The reason for this is that it is not clear what such a theorem should look
like. Formulations in terms of a control-flow graph, like the one by
\cite{abadi_control-flow_2005}, do not take into account temporal properties,
like the well-bracketedness that Example~\texttt{\footnotesize{g1}} relies on.
In fact, our examples show that our logical relation imply a form of
control-flow correctness that is stronger than such formulations, although this
is not made very explicit. As future work, we are considering to look at a more
explicit and useful way to formalise well-bracketed control flow. The idea would
be to define a variant of our capability machine with built-in call and return
instructions and well-bracketed control flow built-in to the operational
semantics, and then prove that compiling such code to our machine using our
calling convention is fully abstract~\cite{abadi_protection_1998}, which roughly
means that the lower-level machine does not allow interactions with the compiled
code that do not correspond to an interaction with the original code in the
high-level machine.

>>>>

\section{Discussion}
\label{sec:discussion}
\subsection{Calling convention}
\textbf{Formulating control flow correctness} While we claim that our calling convention enforces control-flow
correctness, we do not prove a general theorem that shows this, it is not clear what such a theorem should state. Formulations in terms of a control-flow graph, like the one by
\cite{abadi_control-flow_2005}, do not take into account temporal properties,
like the well-bracketedness that Example~\texttt{\footnotesize{g1}} relies on.
In fact, our examples show that our logical relation imply a form of
control-flow correctness that is stronger than such formulations, although this
is not made very explicit. As future work, we consider looking at a more
explicit and useful way to formalise well-bracketed control flow. The idea would
be to define a variant of our capability machine with built-in call and return
instructions and well-bracketed control flow built-in to the operational
semantics, and then prove that compiling such code to our machine using our
calling convention is fully abstract~\cite{abadi_protection_1998}, which roughly
means that the lower-level machine does not allow interactions with the compiled
code that do not correspond to an interaction with the original code in the
high-level machine.
